Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_DNA_methylation.Rmd
fixes reference formatting

The tutorial below is based on WGBS from a species of marine intertebrate (*Montipora capitata* coral) examined in [@https://doi.org/10.1111/1755-0998.13542](#refs), and all raw data can be accessed under NCBI Bioproject PRJNA691891 if you would like to follow the tutorial with this dataset. The general workflow would be consistent for other library preparation and sequencing methods that produce loci-level data. The tutorial indicates places where special analytical consideration should be given to other data types.

@@

---

Vertebrate genomes, on the other hand, have higher overall levels of methylation, with methylation occuring in CpG islands. An example analysis of methylation at individual CG dinucleotides in an elephant shark, mouse, and zebra fish is shown, below.  Results reavel comparable levels of global methyaltion patterns with the majority of sites being highly methylated (≥ 80%), and fewer than one tenth being unmethylated (doi: 10.12688/f1000research.11281.1).

>>>>

The tutorial below is based on WGBS from a species of marine intertebrate (*Montipora capitata* coral) examined in [@https://doi.org/10.1111/1755-0998.13542](#refs), and all raw data can be accessed under NCBI Bioproject PRJNA691891 if you would like to follow the tutorial with this dataset. The general workflow would be consistent for other library preparation and sequencing methods that produce loci-level data. The tutorial indicates places where special analytical consideration should be given to other data types. Given the size of the data files and the computational resources necessary this is not developed to be actionable and reproducible. For context this process outlined below took weeks on a university HPC system.

@@

------------------------------------------------------------------------

Vertebrate genomes, on the other hand, have higher overall levels of methylation, with methylation occuring in CpG islands. An example analysis of methylation at individual CG dinucleotides in the elephant shark, mice, and zebra fish is shown, below. Results reavel comparable levels of global methyaltion patterns with the majority of sites being highly methylated (≥ 80%), and fewer than one tenth being unmethylated (doi: 10.12688/f1000research.11281.1).
